Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
todo + wording

By not taking into account the directivity for directed links, we systematically
make a true positive and a false positive for such links (see a more detailed
discussion about the chosen metric in section \ref{sec:metric}). Therefore,
performance might be improved by predicting an asymmetric adjacency matrix.
Hoping to orientate correctly the most obvious directed links, we attempt to
retrieve some causal information, i.e. the directivity of the links, by computing
and stacking with our symmetric adjacency matrix a matrix of pairwise activation
heuristics. This method computes an anti-symmetric activation score $z_{ij}$
based the variation of fluorescence signal of a neuron $j$ due to a neuron $i$
over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function. % TODO say that we use only the 3 first filters for this

>>>>

By ignoring the directivity, we systematically
make a true positive and a false positive for direct link (see a more detailed
discussion about the chosen metric in section \ref{sec:metric}). Therefore,
performance might be improved by predicting an asymmetric adjacency matrix.
Hoping to orientate correctly the most obvious directed links, we attempt to
retrieve some causal information, i.e. the directivity of the links, by computing
and stacking with our symmetric adjacency matrix a matrix of pairwise activation
heuristics. This method computes an anti-symmetric activation score $z_{ij}$
based the variation of fluorescence signal of a neuron $j$ due to a neuron $i$
over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function. % TODO say that we use only the 3 first filters for this

% TODO speak that we should set the diagonal to the minimum to gain some
% performance.
